---
title: "JALSH Momentum Portfolios"
author: "Paul Nheera"
date: "28 July 2018"
output: html_document

---

```{r Load Libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(quantmod)
library(PerformanceAnalytics)
library(rvest)
library(readxl)
library(readr)
library(dygraphs)
library(knitr)
library(kableExtra)
library(ggplot2)
library(reshape2)
library(dplyr)

#install.packages("ggplot2", version='0.9.1')
#remove.packages('PerformanceAnalytics',lib='C:/Users/Paul Nheera/Documents/R/win-library/3.4')
#install.packages('PerformanceAnalytics', version='1.4.3541')

source("momentum_strat.R")
source("portfolio_backtest.R")
source("~/repos/google-finance-database/Functions/get2D.R")
```

```{r Load Data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load Data: 2D matrix of prices.

DailyPrice <- readRDS("~/repos/google-finance-database/DailyPrice.rds")

jalsh_adjusted <- get2D(DailyPrice,'Adjusted')

#Data to xts object:
jalsh_adjusted <- as.xts(jalsh_adjusted[,-1],as.Date(jalsh_adjusted[,1]))

#Clean Data:
jalsh_adjusted <- na.locf(jalsh_adjusted)
```

In this document we take a look at the performance and risk characteristics of momentum porfolios based on the sJSE All Share stock universe. The momentum we are concerned with here is the cross-sectional momentum.

#### Input Parameters:
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
look_back = 3 # Months
holding = 1 # Months
rebalancing = 1 #Months
```

Momentum Period: `r look_back` month(s)
\newline
Holding period: = `r holding` month(s)
\newline
Rebalancing period: = `r rebalancing` month(s)
\newline

```{r message=FALSE, warning=FALSE, include=FALSE}
#Portfolio Weights:
portfolios = MoM_strat(jalsh_adjusted,look_back,holding ,rebalancing,"2007-05-31")

#Run The Backtest on the different quantile portfolios:
port1 = runBacktest(portfolios[,,1],jalsh_adjusted,100000,cashRate = 0,Cost=0)
port2 = runBacktest(portfolios[,,2],jalsh_adjusted,100000,cashRate = 0,Cost=0)
port3 = runBacktest(portfolios[,,3],jalsh_adjusted,100000,cashRate = 0,Cost=0)
port4 = runBacktest(portfolios[,,4],jalsh_adjusted,100000,cashRate = 0,Cost=0)
port5 = runBacktest(portfolios[,,5],jalsh_adjusted,100000,cashRate = 0,Cost=0)

comb = merge.xts(as.xts(port1[,"Total"]),as.xts(port5[,"Total"])); colnames(comb) = c("Long","Short")

#Daily Returns of the Two Portfolios:
ret1 = ROC(port1[,"Total",drop=FALSE]); colnames(ret1) = '1st Quantile'
ret2 = ROC(port2[,"Total",drop=FALSE]); colnames(ret2) = '2nd Quantile'
ret3 = ROC(port3[,"Total",drop=FALSE]); colnames(ret3) = '3rd Quantile'
ret4 = ROC(port4[,"Total",drop=FALSE]); colnames(ret4) = '4th Quantile'
ret5 = ROC(port5[,"Total",drop=FALSE]); colnames(ret5) = '5th Quantile'

#Monthly Nav:
monthly_nav1 = port1[endpoints(port1),"Total",drop=FALSE]
monthly_nav2 = port2[endpoints(port2),"Total",drop=FALSE]
monthly_nav3 = port3[endpoints(port3),"Total",drop=FALSE]
monthly_nav4 = port4[endpoints(port4),"Total",drop=FALSE]
monthly_nav5 = port5[endpoints(port5),"Total",drop=FALSE]

#Monthly Returns:
monthly_ret1 = ROC(monthly_nav1[,"Total",drop=FALSE]); colnames(monthly_ret1) = '1st Quantile'
monthly_ret2 = ROC(monthly_nav2[,"Total",drop=FALSE]); colnames(monthly_ret2) = '2nd Quantile'
monthly_ret3 = ROC(monthly_nav3[,"Total",drop=FALSE]); colnames(monthly_ret3) = '3rd Quantile'
monthly_ret4 = ROC(monthly_nav4[,"Total",drop=FALSE]); colnames(monthly_ret4) = '4th Quantile'
monthly_ret5 = ROC(monthly_nav5[,"Total",drop=FALSE]); colnames(monthly_ret5) = '5th Quantile'
```


#### Quantiles

Performance results for the differernt quantiles based on `r look_back` month(s) momentum with equal weights and a rebalancing period of `r rebalancing` month(s) and holding period of `r holding` month(s).

```{r echo=FALSE, message=FALSE, warning=FALSE}
clrs = rainbow(5)

charts.PerformanceSummary(cbind(monthly_ret1,monthly_ret2,monthly_ret3,monthly_ret4,monthly_ret5),
                          colorset = clrs)

kable(table.AnnualizedReturns(cbind(monthly_ret1,monthly_ret2,monthly_ret3,monthly_ret4,monthly_ret5))) %>% kable_styling("striped")
```

\newpage


```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Optimization:

formation_periods = c(1,3,6,9,12)
holding_periods = c(1,3,6,9,12)

annual_returns = matrix(NA, nrow=length(formation_periods),ncol = length(holding_periods))
colnames(annual_returns) = rownames(annual_returns) = as.character(formation_periods)
standar_deviations = annual_returns
sharpe_ratios = annual_returns


for(f in formation_periods) for(h in holding_periods) {
  
  #Portfolio Weights:
  portfolios = MoM_strat(jalsh_adjusted,f,h ,h,"2007-05-31")
  
  #Run The Backtest on the different quantile portfolios:
  port1 = runBacktest(portfolios[,,1],jalsh_adjusted,1000000,cashRate = 0.05,Cost=0.0050)
  port5 = runBacktest(portfolios[,,5],jalsh_adjusted,1000000,cashRate = 0.05,Cost=0.0050)
  
  #Month End Navs:
  monthly_nav1 = port1[endpoints(port1),"Total",drop=FALSE]
  monthly_nav5 = port5[endpoints(port5),"Total",drop=FALSE]
  
  #Monthly Returns:
  monthly_ret1 = ROC(monthly_nav1[,"Total",drop=FALSE]); colnames(monthly_ret1) = '1st Quantile'
  monthly_ret5 = ROC(monthly_nav5[,"Total",drop=FALSE]); colnames(monthly_ret5) = '5th Quantile'
  
  annual_returns[as.character(f),as.character(h)] = as.numeric(Return.annualized(monthly_ret1))
  standar_deviations[as.character(f),as.character(h)] = as.numeric(StdDev.annualized(monthly_ret1))
  sharpe_ratios[as.character(f),as.character(h)] = as.numeric(SharpeRatio.annualized(monthly_ret1))
  
}
```

```{r}

melted_sharpe_ratios = melt(sharpe_ratios)

melted_sharpe_ratios$Var1 = factor(melted_sharpe_ratios$Var1,
                                   levels = unique(sort(melted_sharpe_ratios$Var1)))

melted_sharpe_ratios$Var2 = factor(melted_sharpe_ratios$Var2,
                                   levels = unique(sort(melted_sharpe_ratios$Var2)))

# melted_sharpe_ratios = melted_sharpe_ratios %>% 
#   mutate_at(vars(-value),"factor", c("levels"=)) %>% 
#   arrange(desc(as.numeric(Var1)),desc(as.numeric(Var2)))


ggheatmap = ggplot(data = melted_sharpe_ratios, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile() +
  geom_text(aes(Var1, Var2, label = round(value,2)), color = "black", size = 4) +
  xlab("Formation Period") +
  ylab("Holding Period")
  

ggheatmap

## Utility Functions from CT8
```